Results Text

### 2024-04-22 Fish Data Analysis/Results_Text.qmd
Text changes

```{r}
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)
library(lme4)
library(sjPlot)
```

@@

@@

nnd_lmer_still <- lmer(NND ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
nnd_s_aov_me <- Anova(nnd_lmer_still)

@@

nnd_lmer_flow <- lmer(NND ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
nnd_f_aov_me <- Anova(nnd_lmer_flow)

@@

polar_lmer_still <- lmer(School_Polar ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
polar_s_aov_me <- Anova(polar_lmer_still)

@@

polar_lmer_flow <- lmer(School_Polar ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
polar_f_aov_me <- Anova(polar_lmer_flow)

@@

speed_lmer_still <- lmer(School_Speed ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
speed_s_aov_me <- Anova(speed_lmer_still)

@@

speed_lmer_flow <- lmer(School_Speed ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
speed_f_aov_me <- Anova(speed_lmer_flow)

@@

groups_lmer_still <- glmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Still Water"),
                           family = poisson)
groups_s_aov_me <- Anova(groups_lmer_still)

@@

groups_lmer_flow <- glmer(Groups ~ Ablation*Darkness + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
                           family = poisson)
groups_f_aov_me <- Anova(groups_lmer_flow)

@@

glmm_school_stats_table <- tibble(Stat = c(rep("NND",6),rep("Polarization",6),rep("Speed",6),rep("Groups",6)),
       Flow_or_Still = rep(c(rep("Still",3) , rep("Flow",3)), 4),
       Condition = rep(c("Ablation","Darkness","Ablation x Darkness"), 8),
       DF = rep(c(rep(length(nnd_lmer_still@resp$y)-3,3),
                  rep(length(nnd_lmer_flow@resp$y)-3,3)),times = 4),
       Chisq = round(c(nnd_s_aov_me$Chisq[1:3],nnd_f_aov_me$Chisq[1:3],
                 polar_s_aov_me$Chisq[1:3],polar_f_aov_me$Chisq[1:3],
                 speed_s_aov_me$Chisq[1:3],speed_f_aov_me$Chisq[1:3],
                 groups_s_aov_me$Chisq[1:3],groups_f_aov_me$Chisq[1:3]),2),

       P_Val = round(c(nnd_s_aov_me$`Pr(>Chisq)`[1:3],nnd_f_aov_me$`Pr(>Chisq)`[1:3],
                 polar_s_aov_me$`Pr(>Chisq)`[1:3],polar_f_aov_me$`Pr(>Chisq)`[1:3],
                 speed_s_aov_me$`Pr(>Chisq)`[1:3],speed_f_aov_me$`Pr(>Chisq)`[1:3],
                 groups_s_aov_me$`Pr(>Chisq)`[1:3],groups_f_aov_me$`Pr(>Chisq)`[1:3]),2),

@@

perp_angle_lmer_close <- lmer(Fish1_Yaw_Heading_PS ~ Ablation*Darkness + (1|Date), data = perp_angle_df %>% filter(Dist_Cat == "Close"))
perp_angle_aov_me_close <- Anova(perp_angle_lmer_close)

@@

perp_angle_lmer_far <- lmer(Fish1_Yaw_Heading_PS ~ Ablation*Darkness + (1|Date), data = perp_angle_df %>% filter(Dist_Cat == "Far"))
perp_angle_aov_me_far <- Anova(perp_angle_lmer_far)

@@

turning_school_stats_table <- tibble(
       Near_or_Far = rep(c(rep("Near",3) , rep("Far",3)), 1),
       Condition = rep(c("Ablation","Darkness","Ablation x Darkness"), 2),
       DF = c(rep(length(perp_angle_lmer_close@resp$y)-3,3),
                  rep(length(perp_angle_lmer_far@resp$y)-3,3)),
       Chisq = round(c(perp_angle_aov_me_close$Chisq[1:3],perp_angle_aov_me_far$Chisq[1:3]),3),
       P_Val = round(c(perp_angle_aov_me_close$`Pr(>Chisq)`[1:3],perp_angle_aov_me_far$`Pr(>Chisq)`[1:3]),3),
       Is_Sig = P_Val < 0.05)

@@

tab_df(turning_school_stats_table, file="turning_stats.doc")

>>>>

```{r}
library(marginaleffects)
library(tidyverse)
library(ggplot2)
library(bbmle) #For ICtab
library(car)
library(ggpubr)
library(ggdist)
library(emmeans)
library(lme4)
library(sjPlot)
```

@@

```{r}
still_school <- school_data %>% filter(Flow == "Still Water")

nnd_lmer_still <- lmer(NND ~ Ablation*Darkness + Trial + (1|Date), data = still_school)
nnd_s_aov_me <- Anova(nnd_lmer_still, type=c("III"))

m1 <- lmer(NND ~ Ablation*Darkness + (1|Date), data = still_school)
m2 <- lmer(NND ~ Ablation*Darkness + Trial + (1|Date), data = still_school)
m3 <- lmer(NND ~ Ablation*Darkness + Trial + (0 + Trial|Date), data = still_school)
m4 <- lmer(NND ~ Ablation*Darkness + Trial+ (0 + Trial|Date) + (1|Date), data = still_school)
m5 <- lmer(NND ~ Ablation*Darkness + (1|Date/Trial) + (1|Date), data = still_school)

AIC(m1,m2,m3,m4,m5) %>% arrange(AIC)

summary(nnd_lmer_still)
nnd_s_aov_me

Anova(m5, type=c("III"))

emmeans(nnd_lmer_still, specs = pairwise ~ Ablation:Darkness)

NND_pred <- predictions(m3, newdata = datagrid(Ablation = c("No Ablation","Ablated"),
         Darkness = c("Light","Dark"),
         Date = unique(still_school$Date),
         Trial = seq(1:max(still_school$Trial)),
         model = nnd_lmer_still))

ggplot(NND_pred, aes(x = Trial, y = estimate, color = Date))+
  geom_line()+
  geom_point(data = still_school, aes(x = Trial, y = NND, color = Date))+
  facet_wrap(~ Ablation+Darkness)+
  theme_light()
```

@@

nnd_lmer_still <- lmer(NND ~ Ablation*Darkness + Trial + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
nnd_s_aov_me <- Anova(nnd_lmer_still, type=c("III"))
nnd_s_aov_me

@@

nnd_lmer_flow <- lmer(NND ~ Ablation*Darkness + Trial + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
nnd_f_aov_me <- Anova(nnd_lmer_flow, type=c("III"))

@@

polar_lmer_still <- lmer(School_Polar ~ Ablation*Darkness + Trial + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
polar_s_aov_me <- Anova(polar_lmer_still, type=c("III"))

@@

polar_lmer_flow <- lmer(School_Polar ~ Ablation*Darkness + Trial + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
polar_f_aov_me <- Anova(polar_lmer_flow, type=c("III"))

@@

speed_lmer_still <- lmer(School_Speed ~ Ablation*Darkness + Trial + (1|Date), data = school_data %>% filter(Flow == "Still Water"))
speed_s_aov_me <- Anova(speed_lmer_still, type=c("III"))

@@

speed_lmer_flow <- lmer(School_Speed ~ Ablation*Darkness + Trial + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
speed_f_aov_me <- Anova(speed_lmer_flow, type=c("III"))

@@

groups_lmer_still <- glmer(Groups ~ Ablation*Darkness + Trial + (1|Date), data = school_data %>% filter(Flow == "Still Water"),
                           family = poisson)
groups_s_aov_me <- Anova(groups_lmer_still, type=c("III"))

@@

groups_lmer_flow <- glmer(Groups ~ Ablation*Darkness + Trial + (1|Date), data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
                           family = poisson)
groups_f_aov_me <- Anova(groups_lmer_flow, type=c("III"))

@@

values_to_grab <- c(2,3,4,5)

glmm_school_stats_table <- tibble(Stat = c(rep("NND",8),rep("Polarization",8),rep("Speed",8),rep("Groups",8)),
       Flow_or_Still = rep(c(rep("Still",4) , rep("Flow",4)), 4),
       Condition = rep(c("Ablation","Darkness","Trial","Ablation x Darkness"), 8),
       DF = rep(c(rep(length(nnd_lmer_still@resp$y)-3,4),
                  rep(length(nnd_lmer_flow@resp$y)-3,4)),times = 4),
       Chisq = round(c(nnd_s_aov_me$Chisq[values_to_grab],nnd_f_aov_me$Chisq[values_to_grab],
                 polar_s_aov_me$Chisq[values_to_grab],polar_f_aov_me$Chisq[values_to_grab],
                 speed_s_aov_me$Chisq[values_to_grab],speed_f_aov_me$Chisq[values_to_grab],
                 groups_s_aov_me$Chisq[values_to_grab],groups_f_aov_me$Chisq[values_to_grab]),2),

       P_Val = round(c(nnd_s_aov_me$`Pr(>Chisq)`[values_to_grab],nnd_f_aov_me$`Pr(>Chisq)`[values_to_grab],
                 polar_s_aov_me$`Pr(>Chisq)`[values_to_grab],polar_f_aov_me$`Pr(>Chisq)`[values_to_grab],
                 speed_s_aov_me$`Pr(>Chisq)`[values_to_grab],speed_f_aov_me$`Pr(>Chisq)`[values_to_grab],
                 groups_s_aov_me$`Pr(>Chisq)`[values_to_grab],groups_f_aov_me$`Pr(>Chisq)`[values_to_grab]),2),

@@

perp_angle_lmer_close <- lmer(Fish1_Yaw_Heading_PS ~ Ablation*Darkness + Trial + (1|Date), data = perp_angle_df %>% filter(Dist_Cat == "Close"))
perp_angle_aov_me_close <- Anova(perp_angle_lmer_close)

@@

perp_angle_lmer_far <- lmer(Fish1_Yaw_Heading_PS ~ Ablation*Darkness + Trial + (1|Date), data = perp_angle_df %>% filter(Dist_Cat == "Far"))
perp_angle_aov_me_far <- Anova(perp_angle_lmer_far)

@@

shapiro.test(resid(perp_angle_lmer_far))

turning_school_stats_table <- tibble(
       Near_or_Far = rep(c(rep("Near",4) , rep("Far",4)), 1),
       Condition = rep(c("Ablation","Darkness","Trial","Ablation x Darkness"), 2),
       DF = c(rep(length(perp_angle_lmer_close@resp$y)-3,4),
                  rep(length(perp_angle_lmer_far@resp$y)-3,4)),
       Chisq = round(c(perp_angle_aov_me_close$Chisq[1:4],perp_angle_aov_me_far$Chisq[1:4]),2),
       P_Val = round(c(perp_angle_aov_me_close$`Pr(>Chisq)`[1:4],perp_angle_aov_me_far$`Pr(>Chisq)`[1:4]),2),
       Is_Sig = P_Val < 0.05)

@@

tab_df(turning_school_stats_table, file="turning_stats.doc")
```
